---
title: "Analysis"
author: "Diamantis Sellis"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output: html_document
---

```{r, loadLibraries, echo = FALSE, warning = FALSE, message = FALSE}
options(tidyverse.quiet = TRUE)
library(tidyverse)
library(cowplot)
dataPath <- file.path(path.expand('~'),'Dropbox','storystructure','data')
figPath <- file.path(path.expand('~'),'Dropbox','storystructure','figs')
```

```{r, loadData, message=FALSE}
allPathsDolmadakia <- read_tsv(file.path(dataPath, "dolmadakia","allPaths.dat"), na = "None")
allPathsOrientExpress <- read_tsv(file.path(dataPath, "orientExpress", "allPaths.dat"), na = "None")
```

## Dolmadakia

Number of alternative paths: `r nrow(allPathsDolmadakia)`
```{r}
table1 <- (allPathsDolmadakia %>% 
  group_by(endType) %>% 
  summarise('Number Of Paths'=n(), 'Mean Path Length' = mean(pathLength), 'Standard Deviation of Path Length' = sd(pathLength)) %>% 
  mutate(percentage = 100*`Number Of Paths`/sum(`Number Of Paths`)))
knitr::kable(table1)
t.test(allPathsDolmadakia$pathLength[allPathsDolmadakia$endType=="good"],
       allPathsDolmadakia$pathLength[allPathsDolmadakia$endType=="bad"],
       alternative = "greater")
```
```{r, pathLength, fig.cap="Distribution of alternative story path lengts"}
fig2a <- (allPathsDolmadakia %>%
  ggplot(aes(x = pathLength, fill = endType)) + 
  geom_histogram(binwidth = 1) + 
  theme_classic() + 
  xlab("Path length (pages)") + 
  ylab("Paths") +
  scale_fill_brewer(name = "Story ending", palette = "Pastel1") + 
  theme(legend.position = c(0.35, 0.8)))
```

```{r, stepsToFirstPause, fig.cap="Distribution of steps until firsta pause", warning=FALSE}
allPathsDolmadakia %>%
  ggplot(aes(x = stepsToFirstPause, fill = endType)) +
  geom_histogram(binwidth = 1) + 
  xlab("Number of steps to first pause (pages)") + 
  ylab("Paths") +
  scale_fill_brewer(name = "Story ending", palette = "Pastel1") + 
  theme_classic()
ggsave(file.path(figPath,'fig3.png'))
```

```{r, numberOfPause}
table1 <- (allPathsDolmadakia %>%
  group_by(endType,numberOfPause) %>% 
  summarise(numberOfPaths = n()) %>% 
  spread(key=numberOfPause, value = numberOfPaths) %>% 
  rename('No Pause'=`0`, 'Story ending' = endType))
knitr::kable(table1)
```


```{r}
CutoffEffect <-  read_csv(file.path(dataPath, "dolmadakia","CutoffEffect.dat"))

fig6a <- (CutoffEffect %>% 
  ggplot(aes(x = Threshold, y = NumberOfPaths)) +
  geom_point() + scale_x_continuous(trans = 'log10') + 
  scale_y_continuous(trans = 'log10')+
  annotation_logticks(sides="lb"))
```

Distribution of pages to flip forward or backward at each choice
```{r}
edgelistDolmadakia <- read_csv(file.path(dataPath, "dolmadakia","edgelist.csv"), na = "None")
fig4a <- (edgelistDolmadakia %>% 
  mutate(difference = target - source) %>% 
  ggplot(aes(x = difference)) + geom_histogram(binwidth = 10))
```

## Orient Express

Number of alternative paths: `r nrow(allPathsOrientExpress)`
Mean path length: `r mean(allPathsOrientExpress$pathLength)`
Standard deviation of path length: `r sd(allPathsOrientExpress$pathLength)`


```{r}
fig2b <- (allPathsOrientExpress %>%
  ggplot(aes(x = pathLength)) +
  geom_histogram(binwidth = 1) + 
  xlab("Path length (pages)") + 
  ylab("Paths") +
  theme_classic())
```

Distribution of pages to flip forward or backward at each choice
```{r}
edgelistOrientExpress <- read_csv(file.path(dataPath, "orientExpress","edgelist.csv"), na = "None")
fig4b <- (edgelistOrientExpress %>% 
  mutate(difference = target - source) %>% 
  ggplot(aes(x = difference)) + geom_histogram(binwidth = 1))
```

```{r}
CutoffEffect <-  read_csv(file.path(dataPath, "orientExpress","CutoffEffect.dat"))

fig6b <- (CutoffEffect %>% 
  ggplot(aes(x = Threshold, y = NumberOfPaths)) +
  geom_point() + scale_x_continuous(trans = 'log10') + 
  scale_y_continuous(trans = 'log10')+
  annotation_logticks(sides="lb"))
```

## Save plots
```{r}
fig1a <- ggdraw() + draw_image(file.path(figPath, "dolmadakia.png"))
fig1b <- ggdraw() + draw_image(file.path(figPath, "orientExpress.png"))

fig5a <- ggdraw() + draw_image(file.path(figPath, "dolmadakiaPathsClustered.png"))
fig5b <- ggdraw() + draw_image(file.path(figPath, "orientExpressPathsClustered.png"))

fig1 <- plot_grid(fig1a, fig1b, labels=c('A','B'), ncol = 2, scale=c(0.9,0.7))
fig2 <- plot_grid(fig2a, fig2b, labels=c('A','B'), ncol =2)
fig4 <- plot_grid(fig4a, fig4b, labels=c('A','B'), ncol =2)
fig5 <- plot_grid(fig5a, fig5b, labels = c('A', 'B'), ncol = 2, scale = c(0.95, 0.8))
fig6 <- plot_grid(fig6a, fig6b, labels = c('A', 'B'))
fig1
fig2
fig4
fig5
fig6
save_plot(file.path(figPath,"fig1.png"), fig1)
save_plot(file.path(figPath,"fig2.png"), fig2)
save_plot(file.path(figPath,"fig4.png"), fig4)
save_plot(file.path(figPath,"fig5.png"), fig5)
save_plot(file.path(figPath,"fig6.png"), fig6)
```